---
title: "Estimating Heterogeneous Price Elasticities
for Newly Launched Fashion Products via
Bayesian Hierarchical Models - Code"
author: "Jackson Cramer"
output: html_document
---
# 1. PACKAGE LOADING

```{r}
library(arrow)
library(dplyr)
library(ggplot2)
library(MASS)
library(INLA)
library(scoringRules)
library(fBasics)
```

# 2. DATA LOADING

```{r}
df_calendar <- read_parquet("../Data/df_calendar.parquet")
df_products <- read_parquet("../Data/df_products.parquet")
df_sales <- read_parquet("../Data/df_sales.parquet")
```

# 3. DATA PREPROCESSING

```{r}
# Merge date table onto sales table
df_dates <- df_sales %>%
  left_join(df_calendar, by = "date_id")

# Drop disruption weeks as they represent a non-recurring event
df_dates <- df_dates %>%
  filter(major_disruption_2023_week == 0)

# Create binary holiday indicators - flagged if day falls within any part of holiday window
df_dates <- df_dates %>%
  mutate(
    is_ramadan = as.integer(
      ramadan_fasting_10_first_days_2023 == 1 |
      ramadan_fasting_10_first_days_2024_2025 == 1 |
      ramadan_3_days_before == 1 |
      ramadan_eve == 1 |
      ramadan_eid_day_1 == 1 |
      ramadan_eid_remaining_days == 1),
    is_sacrifice = as.integer(
      sacrifice_3_days_before == 1 |
      sacrifice_eve == 1 |
      sacrifice_eid_day_1 == 1 |
      sacrifice_eid_remaining_days == 1),
    is_new_year = as.integer(
      new_year_7_days_before == 1 |
      new_year_3_days_before == 1 |
      new_year_day == 1),
    is_mothers_day = as.integer(
      mother_2_days_before == 1 |
      mother_day == 1),
    is_fathers_day = as.integer(
      father_2_days_before == 1 |
      father_day == 1),
    is_valentines = as.integer(
      valentine_2_days_before == 1 |
      valentine_day == 1),
    is_singles_day = as.integer(
      single_1_day_before == 1 |
      single_day == 1),
    is_black_friday = as.integer(black_friday == 1))

# Aggregate data to month-year-product level - quantity summed, price as monthly median,
# holiday indicators set to 1 if holiday occurred at any point that month
df_grouped <- df_dates %>%
  group_by(month, year, product_id) %>%
  summarise(
    quantity_sold   = sum(quantity_sold),
    sales_price     = median(sales_price),
    is_ramadan      = as.integer(any(is_ramadan == 1)),
    is_sacrifice    = as.integer(any(is_sacrifice == 1)),
    is_new_year     = as.integer(any(is_new_year == 1)),
    is_mothers_day  = as.integer(any(is_mothers_day == 1)),
    is_fathers_day  = as.integer(any(is_fathers_day == 1)),
    is_valentines   = as.integer(any(is_valentines == 1)),
    is_singles_day  = as.integer(any(is_singles_day == 1)),
    is_black_friday = as.integer(any(is_black_friday == 1)),
    .groups = "drop")

# Log-transform price for log-log elasticity model
df_grouped <- df_grouped %>%
  mutate(log_price = log(sales_price))

# Join product table to aggregated dataset
df_all <- df_grouped %>%
  left_join(df_products, by = "product_id")

# Drop non-seasonal products - outside scope of analysis
df_all <- df_all %>%
  filter(productseason_name != "NO SEASON")
```

# 4. DISTRIBUTIONAL EVALUATION FOR QUANTITY SOLD

```{r}
# Calculate sample mean and variance of quantity sold
cat("Mean:", mean(df_all$quantity_sold), "\n")
cat("Variance:", var(df_all$quantity_sold))
```

```{r}
# Fit negative binomial distribution to quantity sold and extract mean and size estimates
fit_nb <- fitdistr(df_all$quantity_sold, "negative binomial")
mu_hat <- fit_nb$estimate["mu"]
size_hat <- fit_nb$estimate["size"]

# Plot histogram of quantity sold (truncated at 100 for visual clarity)
hist(df_all$quantity_sold[df_all$quantity_sold <= 100], 
     freq = FALSE,
     breaks = 40,
     main = "",
     xlab = "Quantity Sold",
     col = "lightblue",
     border = "white",
     xlim = c(0, 100))
x_vals <- 0:100

# Overlay histogram with fitted negative binomial distribution
lines(x_vals, 
      dnbinom(x_vals, mu = mu_hat, size = size_hat), 
      col = "darkgreen", lwd = 2)
```

# 5. TRAIN-TEST SPLIT

```{r}
# Set seed for reproducibility
set.seed(123)

# Perform the split, with 80% of products in training set,
# and the remaining 20% in the test set
products <- unique(df_all$product_id)
train_products <- sample(products, 0.8 * length(products))
df_train <- df_all %>% filter(product_id %in% train_products)
df_test  <- df_all %>% filter(!product_id %in% train_products)

# Verify that the split results in about 80% of observations in train and about 20% test
cat("Proportion in training set:", (nrow(df_train) / (nrow(df_train) + nrow(df_test))), "\n")
cat("Proportion in test set:", (nrow(df_test) / (nrow(df_train) + nrow(df_test))))
```

# 6. MODEL FITTING IN INLA

```{r}
# M1: Baseline model - fixed effects only, no product-level heterogeneity
model1 <- inla(
  quantity_sold ~ log_price + 
    is_ramadan + is_sacrifice + is_new_year +
    is_mothers_day + is_fathers_day + is_valentines +
    is_singles_day + is_black_friday +
    productgender_name + productseason_name,
  family = "nbinomial",
  data = df_train,
  control.fixed = list(
    mean = list(log_price = -1), # prior mean: expect negative elasticity
    prec = list(log_price = 1) # prior precision ~ N(-1, 1)
  ),
  control.compute = list(
    # Model comparison metrics
    mlik = TRUE,
    waic = TRUE,
    cpo = TRUE,
    # Store posterior configuration for sampling
    config = TRUE
  ))

# Return model summary
summary(model1)
```

```{r}
# Duplicate category index variable as INLA requires separate index variables for independent random intercept and slope
df_train <- df_train %>%
  mutate(maingroup_name_slope = maingroup_name)

# M2: Random intercepts and slopes per product category, assumed independent and identically distributed (iid) ~ N(0, 1/tau)
model2 <- inla(
  quantity_sold ~ log_price + 
    is_ramadan + is_sacrifice + is_new_year +
    is_mothers_day + is_fathers_day + is_valentines +
    is_singles_day + is_black_friday +
    productgender_name + productseason_name +
    f(maingroup_name, model = "iid") +              # random intercept per category
    f(maingroup_name_slope, log_price, model = "iid"), # random slope on log_price per category
  family = "nbinomial",
  data = df_train,
  control.fixed = list(
    mean = list(log_price = -1),
    prec = list(log_price = 1)
  ),
  control.compute = list(
    mlik = TRUE,
    waic = TRUE,
    cpo = TRUE,
    config = TRUE
  ))

summary(model2)
```

```{r}
# Duplicate product index variable for independent random slope (same approach as M2)
df_train <- df_train %>%
  mutate(product_id_slope = product_id)

# M3: Random intercepts and slopes at both category and product level, assumed iid ~ N(0, 1/tau)
model3 <- inla(
  quantity_sold ~ log_price + 
    is_ramadan + is_sacrifice + is_new_year +
    is_mothers_day + is_fathers_day + is_valentines +
    is_singles_day + is_black_friday +
    productgender_name + productseason_name +
    f(maingroup_name, model = "iid") +             # random intercept per category
    f(maingroup_name_slope, log_price, model = "iid") +  # random slope on log_price per category
    f(product_id, model = "iid") +             # random intercept per product
    f(product_id_slope, log_price, model = "iid"),   # random slope on log_price per product
  family = "nbinomial",
  data = df_train,
  control.fixed = list(
    mean = list(log_price = -1),
    prec = list(log_price = 1)
  ),
  control.compute = list(
    mlik = TRUE,
    waic = TRUE,
    cpo = TRUE,
    config = TRUE
  ))

summary(model3)
```

# 7. SENSITIVITY ANALYSIS OF POPULATION-LEVEL ELASTICITY (B1) USING M3

```{r}
# Function to fit M3 with different priors on B1
fit_prior_sensitivity <- function(prior_mean, prior_prec, label) {
  model <- inla(
    quantity_sold ~ log_price + 
    is_ramadan + is_sacrifice + is_new_year +
    is_mothers_day + is_fathers_day + is_valentines +
    is_singles_day + is_black_friday +
    productgender_name + productseason_name +
    f(maingroup_name, model = "iid") + 
    f(maingroup_name_slope, log_price, model = "iid") + 
    f(product_id, model = "iid") +  
    f(product_id_slope, log_price, model = "iid"),  
    family = "nbinomial",
    data = df_train,
    control.fixed = list(
      mean = list(log_price = prior_mean),
      prec = list(log_price = prior_prec)
    ))
  marginal <- as.data.frame(inla.smarginal(model$marginals.fixed[["log_price"]])) # extract B1
  marginal$prior_spec <- label
  marginal
}

# Run sensitivity analysis with three priors on B1
results <- bind_rows(
  fit_prior_sensitivity(-1, 1,    "Base: N(-1, 1)"),
  fit_prior_sensitivity(0,  0.001, "Vague (default): N(0, 1000)"),
  fit_prior_sensitivity(-1, 4,    "Strong: N(-1, 0.25)"))

# Plot posterior density of B1 by prior specification
ggplot(results, aes(x = x, y = y, colour = prior_spec)) +
  geom_line(linewidth = 0.9) +
  labs(
    title = "",
    x = expression(beta[1]),
    y = "Posterior density",
    colour = "Prior Specification"
  ) +
  theme_minimal() +
  theme(
    axis.title.x = element_text(size = 14),
    axis.title.y = element_text(size = 14),
    plot.title = element_text(size = 15, face = "bold"))
```

# 8. IN-SAMPLE MODEL COMPARISON

```{r}
# Widely Applicable Information Criterion (WAIC)
cat("M1 WAIC =",  model1$waic$waic, "\n")
cat("M2 WAIC =",  model2$waic$waic, "\n")
cat("M3 WAIC =",  model3$waic$waic, "\n\n")

# Negative Log Score of Conditional Predictive Ordinates (NLSCPO)
cat("M1 NLSCPO =", -sum(log(model1$cpo$cpo)), "\n")
cat("M2 NLSCPO =", -sum(log(model2$cpo$cpo)), "\n")
cat("M3 NLSCPO =", -sum(log(model3$cpo$cpo)), "\n\n")

# Marginal Log-Likelihood (MLIK)
cat("M1 mlik =", model1$mlik[1], "\n")
cat("M2 mlik =", model2$mlik[1], "\n")
cat("M3 mlik =", model3$mlik[1])
```

# 9. OUT-OF-SAMPLE MODEL COMPARISON

```{r}
# Calculate continuous ranked probability score (CRPS) for each model on test data

# Step 1: Stack train and test data, setting test responses to NA for INLA to predict
df_combined <- bind_rows(
  df_train,
  df_test |> mutate(quantity_sold = NA))
y_obs_test <- df_test$quantity_sold # Extract response from test set

# Step 2: Specify model formulae (mirrors M1, M2, M3)
formula1 <- quantity_sold ~ log_price + 
    is_ramadan + is_sacrifice + is_new_year +
    is_mothers_day + is_fathers_day + is_valentines +
    is_singles_day + is_black_friday +
    productgender_name + productseason_name
formula2 <- quantity_sold ~ log_price + 
    is_ramadan + is_sacrifice + is_new_year +
    is_mothers_day + is_fathers_day + is_valentines +
    is_singles_day + is_black_friday +
    productgender_name + productseason_name + f(maingroup_name, model = "iid") +
    f(maingroup_name_slope, log_price, model = "iid")
formula3 <- quantity_sold ~ log_price + 
    is_ramadan + is_sacrifice + is_new_year +
    is_mothers_day + is_fathers_day + is_valentines +
    is_singles_day + is_black_friday +
    productgender_name + productseason_name +
    f(maingroup_name, model = "iid") +               
    f(maingroup_name_slope, log_price, model = "iid") +
    f(product_id, model = "iid") +                  
    f(product_id_slope, log_price, model = "iid")
formulae <- list(formula1, formula2, formula3)

# Step 3: Refit each model (M1, M2, M3) on combined data and compute CRPS via posterior sampling
crps_results <- numeric(3)
for(j in 1:3){
  model_pred <- inla(formulae[[j]],
    family = "nbinomial",
    data   = df_combined,
    control.compute = list(config = TRUE), # config=TRUE required for posterior sampling
    control.fixed   = list(
      mean = list(log_price = -1),
      prec = list(log_price = 1)
    ))
  # Draw 500 posterior samples
  post_samples_test <- inla.posterior.sample(500, model_pred)
  # Extract linear predictors for test observations
  eta <- sapply(post_samples_test, function(s) {
    s$latent[1:nrow(df_combined)][-(1:nrow(df_train))]})
  # Extract size parameter for each sample
  sizes <- sapply(post_samples_test, function(s)
    s$hyperpar[["size for the nbinomial observations (1/overdispersion)"]])
  # Simulate predictive draws from negative binomial distribution using posterior samples of parameters
  y_rep_test <- matrix(NA, nrow = nrow(df_test), ncol = 500)
  for(i in 1:500){
    mu <- exp(eta[, i]) # apply inverse log link to obtain raw response
    y_rep_test[, i] <- rnbinom(nrow(df_test), mu = mu, size = sizes[i])
  }
  # Calculate average CRPS across test observations for each model j
  crps_results[j] <- mean(crps_sample(y = y_obs_test, dat = y_rep_test))
  cat("Model", j, "CRPS =", round(crps_results[j], 3), "\n")
}

# Compare CRPS against observed summary statistics
cat("Mean", round(mean(y_obs_test), 3), "\n")
cat("Standard Deviation:", sd(df_test$quantity_sold), "\n")
cat("Range:", range(df_test$quantity_sold))
```

# 10. IN-SAMPLE DIAGNOSTICS OF MODEL M3

```{r}
# Generate 500 posterior predictive samples from M3
n_sims <- 500
y_rep <- matrix(NA, nrow = nrow(df_train), ncol = n_sims)
post_samples <- inla.posterior.sample(n_sims, model3)
for(i in 1:n_sims){
  s <- post_samples[[i]]
  eta  <- s$latent[1:nrow(df_train)]         # extract linear predictor
  mu   <- exp(eta)                           # obtain raw quantity sold by taking inverse log
  size <- s$hyperpar[["size for the nbinomial observations (1/overdispersion)"]]  # extract size parameter
  y_rep[, i] <- rnbinom(nrow(df_train), mu = mu, size = size)}
```

```{r}
# Investigate model calibration

# Compute probability integral transform (PIT) values
y <- df_train$quantity_sold
n <- nrow(df_train)
pit <- numeric(n)
for(i in 1:n){
  pit[i] <- mean(y_rep[i, ] <= y[i])}

# Apply normal quantile transform to PIT values to obtain randomised quantile residuals
pit <- pmin(pmax(pit, 1e-6), 1 - 1e-6) # to avoid infinity from qnorm
rqr <- qnorm(pit)

# PIT histogram
hist(pit, breaks = 20,
     main = "",
     xlab = "PIT",
     ylab = "Frequency",
     col = "lightblue",
     cex.lab = 1.6)
abline(h = n/20, col = "red", lwd = 1.5, lty = 2) # reference line for uniform distribution

# Quantile-Quantile (QQ) plot of randomised quantile residuals
qqnorm(rqr,
       main = "",
       xlab = "Theoretical Quantiles",
       ylab = "Randomised Quantile Residuals",
       cex.lab = 1.6)
qqline(rqr, col = "red", lwd = 1.5, lty = 2) # reference line for perfectly normal distribution
```

```{r}
# Conduct posterior predictive checks - histogram: generated summary statistics, red line: observed summary statistic

# Compute summary statistics of posterior predictive samples
yrepmin <- apply(y_rep, 2, min)
yrepmax <- apply(y_rep, 2, max)
yrepmean <- apply(y_rep, 2, mean)
yrepskewness <- apply(y_rep, 2, skewness)

# Compute summary statistics of observed training data
obs_min <- min(df_train$quantity_sold)
obs_max <- max(df_train$quantity_sold)
obs_mean <- mean(df_train$quantity_sold)
obs_skewness <- skewness(df_train$quantity_sold)

# (a) Maximum
hist(yrepmax, main = "", xlab = "Maximum Quantity Sold",
     col = "skyblue3", border = "white", breaks = 20, cex.lab = 1.6, xlim = c(1000, 6000))
abline(v = obs_max, col = "red", lwd = 2)
title(main = "(a)", adj = 0, cex.main = 1.8)

# (b) Mean
hist(yrepmean, main = "", xlab = "Mean Quantity Sold",
     col = "skyblue3", border = "white", breaks = 20, cex.lab = 1.6, xlim=c(23.7, 25))
abline(v = obs_mean, col = "red", lwd = 2)
title(main = "(b)", adj = 0, cex.main = 1.8)

# (c) Skewness
hist(yrepskewness, main = "", xlab = "Skewness Quantity Sold",
     col = "skyblue3", border = "white", breaks = 20, cex.lab = 1.6, xlim=c(5.5, 20))
abline(v = obs_skewness, col = "red", lwd = 2)
title(main = "(c)", adj = 0, cex.main = 1.8)
```

# 11. OUT-OF-SAMPLE MODEL DIAGNOSTICS

```{r}
# Compute coverage of M3's 95% posterior predictive intervals on test set
# note: y_rep_test from the CRPS loop above, final iteration corresponds to M3
lower    <- apply(y_rep_test, 1, quantile, 0.025)
upper    <- apply(y_rep_test, 1, quantile, 0.975)
coverage <- mean(y_obs_test >= lower & y_obs_test <= upper)
cat("95% CI Coverage:", round(coverage, 3))
```

```{r}
# Compute CRPS by product category on test set

# Compute observation-level CRPS on test set and join associated product group
crps_values <- crps_sample(y = y_obs_test, dat = y_rep_test)
crps_df <- data.frame(
  crps  = crps_values,
  group = df_test$maingroup_name)

# Box plot of CRPS by category (on log scale for ease of visualisation)
ggplot(crps_df, aes(x = group, y = crps, fill = group)) +
  geom_boxplot() +
  scale_y_log10() +
  labs(x = "Category", y = "CRPS (log scale)") +
  theme_minimal() +
theme(
  legend.position = "none",
  axis.text.x = element_text(angle = 45, hjust = 1, size = 12),
  axis.text.y = element_text(size = 12),
  axis.title = element_text(size = 16))
```

```{r}
# Visualise posterior predictive intervals of M3 using one product per category

# Select one representative product per category - the product whose CRPS is closest to the category median
crps_df$product_id <- df_test$product_id
median_products <- crps_df %>%
  group_by(group) %>%
  slice_min(abs(crps - median(crps)), n = 1,  with_ties = FALSE) %>% # take first if tied
  ungroup()
selected_ids <- median_products$product_id

# Compute 95% posterior predictive intervals and median prediction for selected products,
# with observations ordered by increasing median predicted quantity sold within each category
posterior_pred_df <- df_test %>%
  mutate(
    lower = apply(y_rep_test, 1, quantile, 0.025),
    upper = apply(y_rep_test, 1, quantile, 0.975),
    median_pred = apply(y_rep_test, 1, median),
    obs_index = row_number()
  ) %>%
  filter(product_id %in% selected_ids) %>%
  arrange(maingroup_name, median_pred) %>%
  mutate(obs_index = row_number())

# Plot 95% predictive intervals (blue ribbon), median prediction (blue line),
# and observed quantity sold (red points), faceted by product category
ggplot(posterior_pred_df, aes(x = obs_index)) +
  geom_ribbon(aes(ymin = lower, ymax = upper), alpha = 0.3, fill = "blue") +
  geom_line(aes(y = median_pred), colour = "blue") +
  geom_point(aes(y = quantity_sold), colour = "red", size = 1) +
  facet_wrap(~ maingroup_name, scales = "free") +
  labs(x = "Observation Index", y = "Quantity Sold") +
  theme_minimal() +
  theme(axis.text.x = element_blank(),
    axis.text.y = element_text(size = 12),
    axis.title = element_text(size = 16),
    strip.text = element_text(size = 11))
```

# 12. FIXED AND RANDOM EFFECTS ANALYSIS

```{r}
# Investigate fixed effects of M3
summary(model3)
```

```{r}
# Visualise product-level random effects of M3

# (a) Random intercepts
intercepts <- model3$summary.random$product_id # extract product-level random intercepts from M3
intercepts$product <- 1:nrow(intercepts)
intercepts <- intercepts[sample(nrow(intercepts), 100), ] # select 100 products randomly for ease of visualisation

# Caterpillar plot of random intercept effects, ordered by increasing posterior mean
# Points are posterior means, error bars are 95% credible intervals, red reference line at estimate of 0
ggplot(intercepts, aes(x = reorder(product, mean), y = mean)) +
  geom_point(size = 0.5) +
  geom_errorbar(aes(ymin = `0.025quant`, ymax = `0.975quant`),
                width = 0, alpha = 0.3) +
  geom_hline(yintercept = 0, linetype = "dashed", colour = "red") +
  coord_flip() +
  labs(title = "(a)",
       x = "Product Index", y = "Random Intercept Estimate") +
  theme_minimal() +
  theme(axis.text.y = element_blank(),
        axis.ticks.y = element_blank(),
        axis.text.x = element_text(size = 16),
        axis.title = element_text(size = 16),
        plot.title = element_text(size = 20, hjust = 0),
        panel.grid = element_blank(),
        panel.border = element_rect(colour = "black", fill = NA))

# (b) Random slopes (same process as plot (a) except with slope, not intercept)
slopes <- model3$summary.random$product_id_slope
slopes$product <- 1:nrow(slopes)
slopes <- slopes[sample(nrow(slopes), 100), ]

ggplot(slopes, aes(x = reorder(product, mean), y = mean)) +
  geom_point(size = 0.5) +
  geom_errorbar(aes(ymin = `0.025quant`, ymax = `0.975quant`),
                width = 0, alpha = 0.3) +
  geom_hline(yintercept = 0, linetype = "dashed", colour = "red") +
  coord_flip() +
  labs(title = "(b)",
       x = "Product Index", y = "Random Slope Estimate") +
  theme_minimal() +
  theme(axis.text.y = element_blank(),
        axis.ticks.y = element_blank(),
        axis.text.x = element_text(size = 16),
        axis.title = element_text(size = 16),
        plot.title = element_text(size = 18, hjust = 0),
        panel.grid = element_blank(),
        panel.border = element_rect(colour = "black", fill = NA))
```

```{r}
# Investigate category-level random effects of M3

# Extract random intercept effects for each product category
model3$summary.random$maingroup_name

# Extract random slope effects for each product category
model3$summary.random$maingroup_name_slope
```

# 13 - Demonstrate Elasticity Estimation Using Random Effects

```{r}
# Randomly select one product from the training set (seen) and one from the test set (unseen)

# Set seed for reproducibility
set.seed(123)

train_product <- sample(train_products, 1)
test_product <- sample(df_test$product_id, 1)

# Extract population-level elasticity estimate
b1 <- model3$summary.fixed["log_price", ]$mean
```

```{r}
# Demonstration of elasticity estimation for seen product

# Extract main group of randomly selected seen product
group_seen <- df_train[df_train$product_id == train_product, ]$maingroup_name[1]

# Extract main group slope coefficient estimate from M3
u1g_seen <- model3$summary.random$maingroup_name_slope[
  model3$summary.random$maingroup_name_slope$ID == group_seen, ]$mean

# Extract product slope coefficient estimate from M3
v1i <- model3$summary.random$product_id_slope[
  model3$summary.random$product_id_slope$ID == train_product, ]$mean

# Compute estimate via sum of effects
cat("Elasticity Estimate (seen):", b1 + u1g_seen + v1i, "\n")

# Obtain 95% posterior credible interval of estimate

# Draw 500 posterior samples from M3
samples <- inla.posterior.sample(500, model3)
# Extract effect estimates from each sample
beta1_draws <- sapply(samples, function(s)
  s$latent["log_price:1", ])
u1g_draws_seen <- sapply(samples, function(s)
  s$latent[paste0("maingroup_name_slope:",
    which(model3$summary.random$maingroup_name_slope$ID == group_seen)), ])
v1i_draws <- sapply(samples, function(s)
  s$latent[paste0("product_id_slope:",
    which(model3$summary.random$product_id_slope$ID == train_product)), ])
# Sum sampled effects and compute credible interval
total_draws <- beta1_draws + u1g_draws_seen + v1i_draws
ci <- quantile(total_draws, c(0.025, 0.975))
cat("95% CI (seen):", ci)
```

```{r}
# Demonstration of elasticity estimation for unseen product (same process an seen, but exclude product-level effect estimate)

group_unseen <- df_test[df_test$product_id == test_product, ]$maingroup_name[1]
u1g_unseen <- model3$summary.random$maingroup_name_slope[
  model3$summary.random$maingroup_name_slope$ID == group_unseen, ]$mean

# Compute estimate via sum of effects (exclude v1i, use same b1 as seen)
cat("Elasticity Estimate (unseen):", b1 + u1g_unseen, "\n")

u1g_draws_unseen <- sapply(samples, function(s)
  s$latent[paste0("maingroup_name_slope:",
    which(model3$summary.random$maingroup_name_slope$ID == group_unseen)), ])
total_draws <- beta1_draws + u1g_draws_unseen # exclude v1i, use same beta1_draws as seen
ci_unseen <- quantile(total_draws, c(0.025, 0.975))
cat("95% CI (unseen):", ci)
```
